### 2021-09-02 documentos/pce.tex
Fixed unnecessary bug.

A remarkable consequence of positivity 
\subsection{Single qubit case} % {{{
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i r_i
\end{equation}
where $\tau_k$ is either $1$ or $0$. A direct evaluation of the

@@

\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}

The density matrix $\rho$ of a system of $n$ qubits can be written in Pauli matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $r_{0,\ldots,0}=1$ ($\Tr\rho=1$) and $\sigma_0=\openone$.
We may and will refer to $\paulicomponents$ as the ``Pauli components'' of the 
density matrix of a sistem of qubits.

Let us now define a Pauli component erasing (PCE) operation. A linear operation 
$\mcE$ that acts on a density matrix $\rho$ of a system of qubits is a PCE operation if 
it transforms the Pauli components of $\rho$ as 
\begin{equation}
\begin{split}
	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{split}
\end{equation}
%\ddnote{hay un typo en esta ecuacion}
A PCE operation is a trace-preserving operation that leaves invariant or erases 
the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
todo claro y no hay problema en dejarlo así por el momento.}

@@

>>>>

A remarkable consequence of positivity 
\subsection{Single qubit case} % {{{
\label{sec:single:qubit}
\todo{David escribe una primera version y luego Carlos itera}
Let us discuss the single qubit case of \pce{} maps, they are defined by its action over Bloch vectors, providing that
\begin{equation}
\rho=\frac{\one +\vec r \cdot \vec \sigma}{2},
\end{equation}
then they are defined as follows
\begin{equation}
r_i \mapsto \tau_i r_i
\end{equation}
where $\tau_k$ is either $1$ or $0$. A direct evaluation of the

@@

\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}

The density matrix $\rho$ of a system of $N$ qubits can be written in Pauli
matrices basis as 
\begin{equation}\label{eq:N_qubits_rho}
	\rho =\frac{1}{2^N} 
            \sum_\valpha r_\valpha \sigma_\valpha,
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
%             \sum_{\alpha_1,\ldots,\alpha_N=0}^3 \paulicomponents
% 	\sigma_{\alpha_1}\otimes \ldots \otimes \sigma_{\alpha_N},
	%r_{0,\ldots,0}=1,
\end{equation}
where $\vec \alpha$ denotes a multi index with $N$ components, 
$\sigma_{\vec \alpha} := \sigma_{\alpha_1}\otimes \ldots \otimes
\sigma_{\alpha_N}$ is the tensor product of Pauli matrices and 
$r_{\vec \alpha}$ is the coefficient corresponding to the expansion
of the density matrix in the complete orthonormal basis $\{ \sigma_{\vec
\alpha} \}$. In the sum, each of the $N$ components of $\valpha$, i.e.
$\alpha_{1,\cdots,N}$ is varied from $0$ to $3$. 
Notice that $\sigma_{\vec 0} = \openone$ and since both $\tr \rho=1$ and 
$\tr \sigma_\valpha=\delta_{\valpha,\vec 0}$, $r_{\vec 0}=1$. 
We shall refer to $\paulicomponents$ as the ``Pauli components'' of the density
matrix of a system of qubits.

%  $r_{\vec \alpha} =  $
% where $r_{0,\ldots,0}=1$ ($\Tr\rho=1$) and $\sigma_0=\openone$.

Consider the linear operations that simply attenuate the Pauli components of 
a multiqubit system:
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
\end{equation}
These operations have been studied in \cite{} \cpnote{davalos, dale aca un pequeño 
rollo relevante quiza de una o dos frases. También debemos tener un nombre pues lo de la diagonazliación 
funciona para eso y quizá también seran relevantes para la parte de decoherencia}.
To preserve the trace of the density matrix, we require that 
$\tau_{\vec 0}=1$. 
\cpnote{Tocará ajustar el texto de acuerdo a lo que ponga Davalos aca}
A Pauli component erasing (PCE) operation is a \cpnote{Pauli diagonal operation}
%  A linear operation 
% $\mcE$ 
that either preserves or completely erases the Pauli components of a
density matrix. That is, 
% it transforms its Pauli components as 
\begin{equation}
% \begin{split}
% 	\paulicomponents \mapsto \ \taus \paulicomponents,\hspace{.5cm}\\
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1.
	\paulicomponents \mapsto \taus \paulicomponents,\quad 
	\taus = 0,1.
% \end{split}
\end{equation}
It is worth noticing that not all PCE maps are quantum operations. For single 
qubits, if just one of the $\taus=0$, the complete positivity condition 
is not met, as discussed in \sref{sec:single:qubit}. It will be of central interest
in this article to determine with $\taus$ lead to a valid quantum map.

%\ddnote{hay un typo en esta ecuacion}
% A PCE operation is a trace-preserving operation that leaves invariant or erases 
% the Pauli components of a density matrix of $n$ qubits. \janote{Ojo que aquí 
% habrá que unificar la notación de subíndices. No lo hago porque no lo tengo del 
% todo claro y no hay problema en dejarlo así por el momento.}
\cpnote{Aca voy}

@@

% }}}
